\documentclass[../cv.tex]{subfiles}
\begin{document}
\noindent
\Large
\textbf{Adrian Ng, MSc.}
\newline
\small
Junior Metadata Engineer at IAG Cargo
\newline
\begin{description*}
	\item[Email:] \href{mailto:contact@adrian.ng}{contact@adrian.ng}
	\item[Portfolio:] \href{https://adrian.ng}{adrian.ng}
	\item[Location:] Harrow
\end{description*}
\hfill
\vspace{0.25cm}
\noindent
\newline
\begin{minipage}[t]{0.5\linewidth}
	\section{Profile}
	Not job hunting. But I like to keep track of my work. So I do keep this document updated. But also no care is being taken with regard to its length. \textit{Not job hunting.}
	\par\quad

	I am the \textit{Junior Metadata Engineer} at IAG Cargo, based at Heathrow. We do air-freight. I work in the Data \& Analytics team. My job is to figure out our metadata management solution. It's an exciting journey. Along the way I am building data models and import processes.
	\par\quad

	This document is written in \LaTeX. A typesetting/markup language which also happens to be \href{https://www.overleaf.com/learn/latex/Articles/LaTeX_is_More_Powerful_than_you_Think_-_Computing_the_Fibonacci_Numbers_and_Turing_Completeness}{Turing-complete}.

	I enjoy writing documentation. At work I mostly use Markdown.
	\par\quad

	- Adrian
\end{minipage}
\hspace{0.2cm}
\begin{minipage}[t]{0.3\linewidth}
	\section{Education}
	\textbf{Royal Holloway} \hfill 2017
	\newline
	\textit{Data Science \& Analytics}
	\begin{itemize}[leftmargin=*, itemsep=0.1em]
		\item	Master of Science
		\item	Pass with Distinction
		\item 	Department of Computer Science
	\end{itemize}
	\vspace{0.15cm}
	\textbf{King's Collge London} \hfill 2010
	\newline
	\textit{Mechanical Engineering}
	\begin{itemize}[leftmargin=*, itemsep=0.1em]
		\item Bachelor of Engineering
		\item Upper Second Class with Honours
		\item School of Engineering
	\end{itemize}
\end{minipage}
\hspace{0.2cm}
\begin{minipage}[t]{0.15\linewidth}
	\section{Coding}
	\begin{itemize}[leftmargin=*]
		\item T-SQL, PLSQL		
		\item Java 8		
		\item Powershell		
	\end{itemize}
	\section{Tools}
	\begin{itemize}[leftmargin=*]
%		\item IntelliJ IDEA
%		\item MS SQL Server
		\item VS Code
		\item Git		
		\item Markdown
		\item Jira
%		\item Maven
%		\item WSL
	\end{itemize}
\end{minipage}
\end{document}