\documentclass[../cv.tex]{subfiles}
\begin{document}
\section{IAG Cargo}
\textit{Junior Metadata Engineer}
\hfill
\textit{Data Platform Team}
\hfill
\textit{June 2019 - Present}
\begin{description}[style=multiline, leftmargin=3.5cm]
	\item[Prototype Implementation\\\textnormal{PL/SQL}] Implemented data processes originally prototyped by Data Exploitation team in Alteryx/Tableau
	      \begin{itemize}
		      \item Achieved computational efficiencies where possible:
		            \begin{itemize}
			            \item Computed \textit{directed network graphs} using \texttt{CROSS JOIN} and recursive in-line queries.
			            \item Made use of \textit{materialized views} and \textit{global temp tables} to cache datasets
			            \item Utilized PL/SQL as a functional language with table-valued functions.
		            \end{itemize}
		      \item Specified standards for Data Exploitation team to follow (documentation, UAT evidence, naming conventions, ownership)
	      \end{itemize}
	\item[Self-Service Data Ingestion\\\textnormal{Python, Powershell}]
	      Built an automated data ingestion service enabling Data Analysts to set up their own data pipelines.
		  \begin{itemize}
			\item Utilized by Data Exploitation team across numerous projects.
		      \item Time-series analysis used to visualize undesirably large or small imports in Tableau.
		      \item Provided documentation on:
		            \begin{itemize*}
			            \item local/remote(RDP) installation
			            \item \texttt{yaml} configuration
		            \end{itemize*}
	      \end{itemize}
	\item[Sales Relational Model\\ \textnormal{Oracle}]
	      Modelled the relationship between entities: sales agent/customer/location
	      \begin{itemize}
		      \item Established pipeline between Business Managers (upserts) and Data Analysts (dashboards)
		      \item Relational design enabled efficient ETL automation, constant uptime and immediate retrieval.
	      \end{itemize}
	\item[Training \& Documentation \\ \textnormal{Markdown}]
		\begin{itemize}
		\item Prepared training materials and hosted workshops for analysts on SQL fundamentals
		\item Part of editorial committee to establish an internal Wiki. Conducted interviews for content.
		\item Produced documentation on edge-case and greenfield subject matter:
	      \begin{itemize}
		      \item XML parsing in Oracle
		      \item SSHing to remote Python environment
		      \item Metadata Management (for non-technical C-level audience)
		  \end{itemize}
		\end{itemize}
	      %\item[Metadata Management] I am producing the vision for our Metadata Management solution. That is, \textit{what do we want our solution to look like?} This involves researching and interviewing subject matter experts to populate a Data Glossary, creating policies and rules, visualising  Data Lineage in the Metadata Repository (Atlas, Collibra, Watson Data Catalog)
	      %\item[Mentoring \textnormal{moving-ahead.org}] As part of a British Airways's initiative, I am voluntarily mentoring a colleague. This remote engagement will continue over a 9 month period.
\end{description}
\end{document}